### 2017-09-03 sections/math.tex
Fix equation 2 - replace n with p

From the definition of SVD in (\ref{eq:svd-def}) and from the properties of SVD, the fact follows that a matrix can be represented in the form of its SVD components as a sum of $n$ rank-1 matrices

\begin{equation}
\mtrx{A}=\sum_{i=1}^{n} s_{i}\mathbf{u}_{i}\mathbf{v}_{i}^{\mathsf{T}},
\label{eq:svd-expansion}
\end{equation}

\noindent
where $s_i$ is the $i$-th singular value, $\mathbf{u}_i$ and $\mathbf{v}_i$ are corresponding singular vectors, and $n$ is the rank of matrix~$\mtrx{A}$. Considering the fact that singular values are ordered $s_{1} \geq s_{2} \geq s_{3} \geq ... \geq s_{n}$, the above formula implies that the first term of the sum would have the highest contribution and the last term would have the lowest contribution to matrix~$\mtrx{A}$. Therefore, if we take only first $r$ members of the above summation we get an approximation matrix

@@

Quality of approximation depends on the magnitude of the singular values omitted from the approximation formula, namely $s_{r+1} ...  s_{n}$. The compression algorithm is based on an assumption that the first singular value is order-of-magnitude higher than singular values at the end of the decomposition sequence. In special cases, when $r=n$, or $s_{i}=0$ for all $i > r$, the omitted singular values do not contribute to the sum and the compression is therefore lossless. In other cases, approximation error has to be calculated and taken into account to avoid loss of important details in data.

@@

\noindent
where $m$ and $n$ are dimensions of matrix $\mtrx{A}$. Explanation of the compression ratio formula is best done using Figure~\ref{fig:lowrank_svd}. Light color represents the part of matrix decomposition that is to be stored in the output file as a low-rank approximation of the input.

>>>>

From the definition of SVD in (\ref{eq:svd-def}) and from the properties of SVD, the fact follows that a matrix can be represented in the form of its SVD components as a sum of $p$ rank-1 matrices

\begin{equation}
\mtrx{A}=\sum_{i=1}^{p} s_{i}\mathbf{u}_{i}\mathbf{v}_{i}^{\mathsf{T}},
\label{eq:svd-expansion}
\end{equation}

\noindent
where $s_i$ is the $i$-th singular value of matrix $\mtrx{A}$, $\mathbf{u}_i$ and $\mathbf{v}_i$ are corresponding singular vectors of matrix $\mtrx{A}$, and $p = \mathrm{min}(m, n)$. Considering the fact that singular values are ordered $s_{1} \geq s_{2} \geq s_{3} \geq ... \geq s_{p}$, the above formula implies that the first term of the sum would have the highest contribution and the last term would have the lowest contribution to matrix~$\mtrx{A}$. Therefore, if we take only first $r$ members of the above summation we get an approximation matrix

@@

Quality of approximation depends on the magnitude of the singular values omitted from the approximation formula, namely $s_{r+1} ...  s_{p}$. The compression algorithm is based on an assumption that the first singular value is order-of-magnitude higher than singular values at the end of the decomposition sequence. In special cases, when $r=p$, or $s_{i}=0$ for all $i > r$, the omitted singular values do not contribute to the sum and the compression is therefore lossless. In other cases, approximation error has to be calculated and taken into account to avoid loss of important details in data.

@@

\noindent
where $m$ is the number of rows and $n$ is the number of columns of matrix $\mtrx{A}$. Explanation of the compression ratio formula is best done using Figure~\ref{fig:lowrank_svd}. Light color represents the part of matrix decomposition that is to be stored in the output file as a low-rank approximation of the input.
